Unlocking Sensitivity for Visibility-based Estimators of the 21\,cm Reionization Power Spectrum

### 2017-07-24 Rotation paper/draft_working.tex
save

Selecting $\psi_\nu$ to be a linear function of $\nu$ allows one to cancel
%To linear order in $\nu$, $\psi_\nu$ cancels
the decoherence due to the two visibilities having different phase centers. By default the correlators of a drift-scan array phase the two visibilities both to zenith at the same time. When they are cross-multiplied with a time lag, the visibilities must be rephased before the delay transform to account for the movement of the phase center. The effect of the phase thus roughly corresponds in a shift of the delay mode measured, and we should expect $\psi_{\nu}$ to be approximately a linear function of $\nu$:
\[
\psi_{\nu}\sim 2\pi\Delta\tau\nu,
\]
where $\Delta\tau$ is a shift in delay corresponding to the phase center movement.

In Fig. \ref{fig:phi_nu} we show the phases of $\Theta_\nu$ at the optimal time offset, i.e. when $|\Theta_\nu|$ is maximized. The phases are shown for the baseline pair \{2,0:2,1\} of PAPER-128. The drift-scan phase dependence is compared with that of the same baseline with hypothetical tracking-elements (Eq. \eqref{eq:Thetanu} and Eq. \eqref{eq:Thetanu_tracking}). In the drift-scan case, we indeed see a linear relation corresponding to a delay of $\Delta\tau\approx15.7$\,ns. This delay corresponds to the light travel time from one antenna to another of the rotated baseline. In the tracking case, since the phase center is fixed to the sky, only second order effects are observed. The origin of the second order effects can be seen as due to the $w$-term, or more precisely the fact that $uvw$ tracks do not cross when their two-dimensional projections do. We refer the reader to Appendix \ref{sec:appA} for further explanation. In both cases, the full effects are encapsulated in the phase of $\Theta_\nu$ and can be thus determined empirically without any additional computation.

>>>>

Selecting $\psi_\nu$ to be a linear function of $\nu$ allows one to cancel
%To linear order in $\nu$, $\psi_\nu$ cancels
the decoherence due to the two visibilities having different phase centers. By default the correlators of a drift-scan array phase the two visibilities both to zenith at the same time. When they are cross-multiplied with a time lag, the visibilities must be rephased before the delay transform to account for the movement of the phase center. The effect of the phase thus roughly corresponds in a shift of the delay mode measured, and we should expect $\psi_{\nu}$ to be approximately a linear function of $\nu$:
\[
\psi_{\nu}\sim 2\pi\Delta\tau\nu,
\]
where $\Delta\tau$ is a shift in delay corresponding to the phase center movement, more precisely the light travel time from one antenna to another of the rotated baseline (relative to the phase center).

In Fig. \ref{fig:phi_nu} we show the phases of $\Theta_\nu$ at the optimal time offset, i.e. when $|\Theta_\nu|$ is maximized. The phases are shown for the baseline pair \{2,0:2,1\} of PAPER-128. The drift-scan phase dependence is compared with that of the same baseline with hypothetical tracking-elements (Eq. \eqref{eq:Thetanu} and Eq. \eqref{eq:Thetanu_tracking}). In the drift-scan case, we indeed see a linear relation corresponding to a delay of $\Delta\tau\approx15.7$\,ns.  In the tracking case, since the phase center is fixed to the sky, only second order effects are observed. The origin of the second order effects can be seen as due to the $w$-term, or more precisely the fact that $uvw$ tracks do not cross when their two-dimensional projections do. We refer the reader to Appendix \ref{sec:appA} for further explanation. In both cases, the full effects are encapsulated in the phase of $\Theta_\nu$ and can be thus determined empirically without any additional computation.
